Download data

### 2024-05-03 scripts/subsetDataforCrews.Rmd
working towards fn to split by stz

unique(seed_zones$stz)

lapply(teams_list[13], project_maker,
       admu = admin_boundaries, 
       target_species = spp_needed, 
       blm_surf = blm_surf, 
       fs_surf = usfs_surf, 
       fire = fire_perimeters, 
       invasive = invasives, 
       total_change = change_intensity, 
       occurrences = occurrences, 
      # historic_SOS, 
       roads = roads, seed_transfer = STZ)

>>>>

lapply(teams_list[13], project_maker,
       admu = admin_boundaries, 
       target_species = spp_needed, 
       blm_surf = blm_surf, 
       fs_surf = usfs_surf, 
       fire = fire_perimeters, 
       invasive = invasives, 
       total_change = change_intensity, 
       occurrences = occurrences, 
       roads = roads, seed_transfer = STZ)
